\documentclass{homeworg}
\usepackage{array}
\usepackage{threeparttable}
\usepackage{geometry}
\usepackage{float}
\usepackage{fancyhdr,lastpage}
\usepackage[format=hang,font=normalsize,labelfont=bf]{caption}
\usepackage{listings}
\usepackage{setspace}
\renewcommand{\baselinestretch}{1.0}
\lstset{frame=single,
  language=MATLAB,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  breaklines=true,
  breakatwhitespace=true
  tabsize=3
}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{harvard}
\usepackage{setspace}
\usepackage{float,color}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{xparse}


\DeclareMathOperator*{\argmax}{argmax} % thin space, limits underneath in displays


\title{Notes on AFFGT(2021) Replication}
\author{Linghui Wu}

\begin{document}

\maketitle

\section{Open Economy Equilibrium}

\subsection{Equilibrium Conditions}


\textbf{Calibrated Parameters}

The values for the calibrated parameters are taken from Table 1 on page 20 when solving the equilibrium. To be specific, they are substitution elasticities $\theta = 4$ and $\sigma = 4$, fixed costs $f^{u} = 1$ and $f^{d} = 1$,  labor intensities $\alpha^{u} = 1$ and $\alpha^{d} = 0.5483$, scaled population $L^{us} = 0.4531$ and $L^{row} = 9.5469$, productivities $A^{u}_{us} = A^{d}_{us} = 1$, $A^{u}_{row} = 0.1121$ and $A^{d}_{row} = 0.2752$, and iceberg trade costs $\tau_d = 3.0066$ and $\tau_u = 2.5731$. Tax $t^{s}_{ij}$ and subsidises $v^{s}_{ij}$ where $s \in \{u, d\} \text{ and } i, j \in \{H, F\}$ are exogenous and set to be zeros. I consider solving the model with both U.S. wages being normalized as $w_{us} = 1$ and not being normalized.

\textbf{Characterizing Equations}

I follow Appendix A to pin down the equations that characterize the open economy equilibrium. Here, I further simplify and reorder the non-linear system of equations so that the variables can be expressed in terms of the known parameters and the pre-defined variables.

\begin{itemize}[ref=Step \arabic{enumi}, wide=0pt]
\item Price in the upstream sectors: $(p^{u}_{ii}, p^{u}_{ij}, p^{u}_{jj}, p^{u}_{ji})$.
\begin{equation}
\begin{aligned}
\label{eq:p_u}
mc^{u}_{i} &= \frac{\bar{\alpha^{u}}}{A^{u}_{i}}w^{\alpha^{u}}(P^{u}_{i})^{1-\alpha^{u}} = \frac{\bar{\alpha^{u}}}{A^{u}_{i}}w^{\alpha^{u}} \\
p^{u}_{ij} &= \frac{\mu^{u}\tau^{u}_{ij}mc^{u}_{i}}{1+v^{u}_{ij}} = \frac{\mu^{u}\tau^{u}}{1+v^{u}_{ij}}\frac{\bar{\alpha^{u}}}{A^{u}_{i}}w^{\alpha^{u}}
\end{aligned}
\end{equation}
since $\alpha^{u}=1$.
\item Price indexes in the upstream sectors: $(P^{u}_{ii}, P^{u}_{ij}, P^{u}_{jj}, P^{u}_{ji})$ and $(P^{u}_{i}, P^{u}_{j})$.
\begin{equation}
\begin{aligned}
\label{eq:P_u}
P^{u}_{ji} &= [\int_{0}^{M^{u}_{j}}[(1+t^{u}_{ji})p^{u}_{ji}(\omega)]^{1-\theta}d\omega]^{\frac{1}{1-\theta}} = (M^{u}_{j})^{\frac{1}{1-\theta}}(1+t^{u}_{ji})p^{u}_{ji} \\
P^{u}_{i} &= [\Sigma_{j\in\{H, F\}}(P^{u}_{ji})^{1-\theta}]^{\frac{1}{1-\theta}}
\end{aligned}
\end{equation}
\item Price in the downstream sectors: $(p^{d}_{ii}, p^{d}_{ij}, p^{d}_{jj}, p^{d}_{ji})$.
\begin{equation}
\begin{aligned}
\label{eq:p_d}
mc^{d}_{i} &= \frac{\bar{\alpha^{d}}}{A^{d}_{i}}w^{\alpha^{d}}(P^{u}_{i})^{1-\alpha^{d}}\\
p^{d}_{ij} &= \frac{\mu^{d}\tau^{d}_{ij}mc^{d}_{i}}{1+v^{d}_{ij}} = \frac{\mu^{d}\tau^{d}}{1+v^{d}_{ij}}\frac{\bar{\alpha^{d}}}{A^{d}_{i}}w^{\alpha^{d}}(P^{u}_{i})^{1-\alpha^{d}}
\end{aligned}
\end{equation}
by plugging $P^{u}_{i}$ and $P^{u}_{j}$ derived from Equation \ref{eq:P_u}.
\item Price indexes in the downstream sectors: $(P^{d}_{ii}, P^{d}_{ij}, P^{d}_{jj}, P^{d}_{ji})$ and $(P^{d}_{i}, P^{d}_{j})$.
\begin{equation}
\begin{aligned}
\label{eq:P_d}
P^{d}_{ji} &= [\int_{0}^{M^{d}_{j}}[(1+t^{d}_{ji})p^{d}_{ji}(\omega)]^{1-\sigma}d\omega]^{\frac{1}{1-\sigma}} = (M^{d}_{j})^{\frac{1}{1-\sigma}}(1+t^{d}_{ji})p^{d}_{ji} \\
P^{d}_{i} &= [\Sigma_{j\in\{H, F\}}(P^{d}_{ji})^{1-\sigma}]^{\frac{1}{1-\sigma}}
\end{aligned}
\end{equation}
\item Production levels by free entry condition: $(y^{u}_{i}, y^{u}_{j}, y^{d}_{i}, y^{d}_{j})$.
\begin{equation}
\begin{aligned}
\label{eq:y}
y^{d}_{i} &= (\sigma-1)f^{d}_{i} = (\sigma-1)f^{d} \\
y^{u}_{i} &= (\theta-1)f^{u}_{i} = (\theta-1)f^{u}
\end{aligned}
\end{equation}
\item Labor demand in the upstream and downstream sectors: $(\ell^{u}_{i}, \ell^{u}_{j}, \ell^{d}_{i}, \ell^{d}_{j})$.
\begin{equation}
\begin{aligned}
\label{eq:l}
\ell^{u}_{i} &= \frac{f^{u}_{i}+y^{u}_{i}}{A^{u}_{i}} \\
\ell^{d}_{i} &= \alpha^{d}\frac{mc^{d}_{i}(f^{d}_{i}+y^{d}_{i})}{w_{i}}
\end{aligned}
\end{equation}
where $y^{u}_{i}$, $y^{d}_{i}$ and $mc^{d}_{i}$ are from Equations \ref{eq:y} and \ref{eq:p_d}.
\item Quantities and outputs in the upstream sectors: $(Q^{u}_{ii}, Q^{u}_{ij}, Q^{d}_{ji}, Q^{d}_{jj})$ and $(x_{ii}, x_{ij}, x_{ji}, x_{jj})$.
\begin{equation}
\begin{aligned}
\label{eq:Q,x}
Q^{u}_{ij} &= (1-\alpha^{d})\frac{mc^{d}_{i}(f^{d}_{i}+y^{d}_{i})}{P^{u}_{i}}(\frac{P^{u}_{ji}}{P^{u}_{i}})^{-\theta} = (1-\alpha^{d})\frac{mc^{d}_{i}(f^{d}+y^{d}_{i})}{P^{u}_{i}}(\frac{P^{u}_{ji}}{P^{u}_{i}})^{-\theta} \\
x_{ji} &= Q^{u}_{ji}[\frac{(1+t^{u}_{ji})p^{u}_{ji}}{P^{u}_{ji}}]^{-\theta}
\end{aligned}
\end{equation}
\item Outputs in the downstream sectors: $(c_{ii}, c_{ij}, c_{ji}, c_{jj})$.
\begin{equation}
\begin{aligned}
\label{eq:c}
c_{ji} &= \frac{w_{i}L_{i}+T_{i}}{(P^{d}_{i})^{1-\sigma}}[(1+t^{d}_{ji})p^{d}_{ji}]^{-\sigma}
\end{aligned}
\end{equation}
\end{itemize}

\subsection{Solving Non-linear Systems}

To solve the equilibrium allocations, I need $\boldsymbol{x}=(w_{j}, M^{u}_{i}, M^{u}_{j}, M^{d}_{i}, M^{d}_{j}, T_{i}, T_{j})$ be a vector of seven endogenous variables if the wage is normalized and $\boldsymbol{x}=(w_{i}, w_{j}, M^{u}_{i}, M^{u}_{j}, M^{d}_{i}, M^{d}_{j}, T_{i}, T_{j})$ be a vector of eight endogenous variables otherwise\footnote{The corresponding MATLAB scripts are \lstinline{est.m} and \lstinline{solve_eq.m} for the open economy where the wage is not normalized. \lstinline{est_nw.m} and \lstinline{solve_eq_nw.m} are for the open economy where the wage is normalized.}. The equilibrium constraints that I employ for optimizations are as follows\footnote{When the wage is not normalized, the non-linear system is squared with eight unknowns and eight equations and it yields a unique solution. On the other hand, when the wage is not normalized, I utilize the same set of eight equations. Though the number of unknown parameters is fewer than that of the equations, the system still yields a unique solution}.
\begin{itemize}[ref=Step \arabic{enumi}, wide=0pt]
\item Labor market clearing: $(LMC_{i}, LMC_{j})=\boldsymbol{0}$.
\begin{equation}
\begin{aligned}
\label{eq:lmc}
LMC_{i} &= L_{i}-M^{d}_{i}*\ell^{d}_{i}-M^{u}_{i}*\ell^{u}_{i}
\end{aligned}
\end{equation}
\label{eq:gmc}
\item Good market clearing: $(GMC^{u}_{i}, GMC^{u}_{j}, GMC^{d}_{i}, GMC^{d}_{j})=\boldsymbol{0}$.
\begin{equation}
\begin{aligned}
\label{eq:gmc}
GMC^{u}_{i} &= y^{u}_{i}-M^{d}_{i}x_{ii}-M^{d}_{j}\tau^{u}_{ij}x_{ij} = y^{u}_{i}-M^{d}_{i}x_{ii}-M^{d}_{j}\tau^{u}x_{ij}\\
GMC^{d}_{i} &= y^{d}_{i}-c_{ii}-\tau^{d}_{ij}c_{ij} = y^{d}_{i}-c_{ii}-\tau^{d}c_{ij}
\end{aligned}
\end{equation}
\item Budget balance: $(BB_{i}, BB_{j})=\boldsymbol{0}$.
\begin{equation}
\begin{aligned}
\label{eq:bb}
BB_{i} &= T_{i} - \Sigma_{j\in\{H,F\}}[t^d_{ji}M^{d}_{j}c_{ji}p^{d}_{ji}+t^{u}_{ji}M^{d}_{i}M^{u}_{j}x_{ji}p^{u}_{ji}-v^{d}_{ij}M^{d}_{i}c_{ij}p^{d}_{ij}-v^{u}_{ij}M^{u}_{i}M^{d}_{j}x_{ij}p^{u}_{ij}].
\end{aligned}
\end{equation}
\end{itemize}

\subsection{Results and Allocations}

I implement \lstinline{fsolve} in MATLAB as the numerical solver \footnote{Due to the restricted access to \lstinline{Knitro}.} with the $\boldsymbol{x} = \boldsymbol{(\sqrt{x}) ^ 2}$ technique to solve the equilibrium allocations. Here, I only report the results when the wage is normalized.

The values for the eight params are
\begin{align*}
\begin{bmatrix}
w_j
\end{bmatrix} &= \begin{bmatrix}
0.1285
\end{bmatrix} \\
\begin{bmatrix}
M^{u}_{i}, M^{u}_{j}, M^{d}_{i}, M^{d}_{j}
\end{bmatrix} &= \begin{bmatrix}
0.0516, 0.1205, 0.0322, 0.0790
\end{bmatrix} \\
\begin{bmatrix}
T_{i}, T_{j}
\end{bmatrix} &= \begin{bmatrix}
4.63e^{-10}, 1.75e^{-10}
\end{bmatrix}
\end{align*}
The optimized parameters are independent of the initial guesses that passed in. "fsolve" finds the right solution and exits because the first-order optimality is small. The diagnostics of the optimization results shows that the sum of the squared function errors "fval" is 7.93e-18 and the sum of absolute "fval" is 4.79e-9. 

Next, I compare the statistics around the zero-tariff equilibrium with those in Table 3 of the draft. Except for discrepency from the numerical precision, the two sets of statistics are nearly the same.

\begin{table}[H]
\centering
\caption{\textbf{Comparison of Statistics around the Zero Tariff Equilibrium}}
\label{tab:stats_compar}
\begin{tabular}{llllllll}
\hline\hline
Statistics   & $\Omega_{H, H}$ & $\Omega_{F, H}$ & $\Omega_{F, F}$ & $\Omega_{H, F}$ & $b^{H}_{H}$ & $b^{H}_{F}$ & $\lambda^{d}_{H}$ \\
\hline
Table 3 & 0.4149 & 0.0368 & 0.4356 & 0.016 & 0.9363 & 0.0617 & 0.993 \\
My Solutions & 0.4150 & 0.0367 & 0.4357 & 0.016 & 0.9383 & 0.0617 & 0.993 \\
\hline\hline
\end{tabular}
\begin{flushleft}
\scriptsize{\textit{Note:} This table contains summary statistics for the endogeneous aggregate variables relevant for the first order approximation around the zero tariff equilibrium. 

$\Omega_{F, H}\equiv\frac{M^{u}_{F}M^{d}_{H}p^{u}_{F, H}x_{F, H}}{M^{d}_{H}(p^{d}_{H,F}c_{H,F}+p^{d}_{H,H}c_{H,H})}$ is the share of Home final-good revenue spend on intermediate input varieties from F. 

$b^{H}_{F}\equiv\frac{M^{d}_{F}p^{d}_{F,H}c^{d}_{F,H}}{w_{H}L_{H}}$ is the share of Home income spend on foreign varieties. 

$\lambda^{d}_{H}\equiv\frac{M^{d}_{H}(p^{d}_{H,F}c_{H,F}+p^{d}_{H,H}c_{H,H})}{w_{H}L_{H}}$ is the ratio of domestic final-good revenue to national income in country H.}
\end{flushleft}
\end{table}

\section{Minor Comments}

A few grammatical errors and typos in the April 24 draft are as follows.

\begin{enumerate}[ref=Step \arabic{enumi}, wide=0pt]

\item On page 6, it says “thus assuming that all firm’s output can used as either for final consumption or as an intermediate input”. It should be “[…] can be used as […]”.

\item On page 36, the last sentence of the first paragraph begins with “Nota that”. It should be “Note that”.

\item In equation (29) on page 36, the integration domain of $P^{u}_{ji}$ should be from $0$ to $M^{u}_{j}$ not to $M^{d}_{j}$.

\item In equation (32) on page 37, the subscript of $c_{ji}$ is flipped. It should be $y^{d}_{i} = c_{ii} + tau^{d}_{ij}c_{ij}$.

\item In equation (34) on page 37, the last term of $T_{i}$ should be $-v^{u}_{ij}M^{d}_{j}M^{u}_{i}x_{ij}p^{u}_{ij}$.

\end{enumerate}

To improve readability, I would suggest specifying on page 36 that

\begin{enumerate}[ref=Step \arabic{enumi}, wide=0pt]

\item $\mu_u = \frac{\theta}{\theta-1}$ and $\mu_d = \frac{\sigma}{\sigma-1}$ in equation (26).

\item $\bar{\alpha^{s}} = \frac{1}{(\alpha^{s})^{\alpha^{s}}(1-\alpha^{s})^{1-\alpha_s}}$ where $s \in \{u, d\}$ in equation (26).

\item $\alpha$ in equations (28) for $Q^{u}_{ij}$ and $\ell^{d}_{i}$is $\alpha^{d}$.

\end{enumerate}

\end{document}
